Federated Imputation

### 2020-07-13 synthesizing_partitioned_data.Rmd
Added partitioned boys data and one fixed seed.

```{r, echo = F, cache=thomcache, cache.lazy=thomlazy}
knitr::kable(summary_out_cart, digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data with m=5 in the last three rows.")
```

@@

```{r, echo = F, cache=thomcache, cache.lazy=thomlazy}
bind_rows("n = 100" = summary_out_cart_part_n100, 
          "n = 1000" = summary_out_cart_part_n1000,
          "n = 10000" = summary_out_cart_part_n10000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
bind_rows("n = 100" = summary_out_norm_part_n100,
          "n = 1000" = summary_out_norm_part_n1000, 
          "n = 10000" = summary_out_norm_part_n10000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of method 'norm' with M = 10 in the last three rows with partitioned data.")

@@

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
bind_rows("n = 100" = cor_summary_out_cart_part_n100, 
          "n = 1000" = cor_summary_out_cart_part_n1000,
          "n = 10000" = cor_summary_out_cart_part_n10000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
bind_rows("n = 100" = cor_summary_out_norm_part_n100, 
          "n = 1000" = cor_summary_out_norm_part_n1000,
          "n = 10000" = cor_summary_out_norm_part_n10000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
source("2.f Synthesize 10 subsets with and without correlations.R")
```

```{r, echo = F}
bind_rows("n = 100" = p10_summary_out_cart_part_n100, 
          "n = 1000" = p10_summary_out_cart_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, echo = F}
bind_rows("n = 100" = p10_summary_out_norm_part_n100, 
          "n = 1000" = p10_summary_out_norm_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, echo = F}
bind_rows("n = 100" = cor_p10_summary_out_cart_part_n100, 
          "n = 1000" = cor_p10_summary_out_cart_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, echo = F}
bind_rows("n = 100" = cor_p10_summary_out_norm_part_n100, 
          "n = 1000" = cor_p10_summary_out_norm_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
source("2.g Synthesize bootstrapped boys data.R")
```

@@

```{r, echo = F}
knitr::kable(summary_cart_10, digits = 3)
```

@@

```{r, echo = F}
#knitr::kable(summary_vs_10, digits = 3)

@@

```{r, include = F}
knitr::kable(broom::tidy(lm(wgt ~ age + hgt, boyscomp), conf.int = T))
```

>>>>

```{r, echo = F}
knitr::kable(summary_out_cart, digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data with m=5 in the last three rows.")
```

@@

```{r, echo = F}
bind_rows("n = 100" = summary_out_cart_part_n100, 
          "n = 1000" = summary_out_cart_part_n1000,
          "n = 10000" = summary_out_cart_part_n10000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, echo = F}
bind_rows("n = 100" = summary_out_norm_part_n100,
          "n = 1000" = summary_out_norm_part_n1000, 
          "n = 10000" = summary_out_norm_part_n10000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of method 'norm' with M = 10 in the last three rows with partitioned data.")

@@

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy, eval = F}
bind_rows("n = 100" = cor_summary_out_cart_part_n100, 
          "n = 1000" = cor_summary_out_cart_part_n1000,
          "n = 10000" = cor_summary_out_cart_part_n10000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, echo = F, cache = thomcache, cache.lazy=thomlazy, eval=F}
bind_rows("n = 100" = cor_summary_out_norm_part_n100, 
          "n = 1000" = cor_summary_out_norm_part_n1000,
          "n = 10000" = cor_summary_out_norm_part_n10000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, include = F, cache=thomcache, cache.lazy=thomlazy, eval=F}
source("2.f Synthesize 10 subsets with and without correlations.R")
```

```{r, echo = F, eval=F}
bind_rows("n = 100" = p10_summary_out_cart_part_n100, 
          "n = 1000" = p10_summary_out_cart_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, echo = F, eval=F}
bind_rows("n = 100" = p10_summary_out_norm_part_n100, 
          "n = 1000" = p10_summary_out_norm_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, echo = F,eval=F}
bind_rows("n = 100" = cor_p10_summary_out_cart_part_n100, 
          "n = 1000" = cor_p10_summary_out_cart_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, echo = F,eval=F}
bind_rows("n = 100" = cor_p10_summary_out_norm_part_n100, 
          "n = 1000" = cor_p10_summary_out_norm_part_n1000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
```

@@

```{r, include = F, cache=thomcache, cache.lazy=thomlazy, eval = F}
source("2.g Synthesize bootstrapped boys data.R")
```

@@

```{r, echo = F, eval = F}
knitr::kable(summary_cart_10, digits = 3)
```

@@

```{r, echo = F, eval = F}
#knitr::kable(summary_vs_10, digits = 3)

@@

```{r, include = F, eval = F}
knitr::kable(broom::tidy(lm(wgt ~ age + hgt, boyscomp), conf.int = T))
```
